\subsection*{Unit 4 Geometry Practice Test}

\setcounter{questionnum}{0}

\noindent\markforreview
\vspace{1em}

The surface area, in square inches, of a cube can be represented by the expression $24a^2$, where $a$ is a positive constant. Which expression represents the volume, in cubic inches, of the cube?

\choicebox{A}{$8a^3$}  
\choicebox{B}{$16a^3$}  
\choicebox{C}{$64a^6$}  
\choicebox{D}{$216a^6$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Given the function $f(x) = \pi x^3 + \pi x^2$, where $f$ represents the volume (in cubic feet) of a right circular cylinder with radius $x$ feet, which expression represents the height (in feet) of the cylinder?

\choicebox{A}{$x + 1$}  
\choicebox{B}{$\pi x^3$}  
\choicebox{C}{$x$}  
\choicebox{D}{$x^3 + 1$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Identical rectangles $X$ and $Y$ each have an area of $\frac{49}{5}$ square meters and a perimeter of $P$ meters. If one of the shorter sides of rectangle $X$ is glued to one of the shorter sides of rectangle $Y$, the resulting rectangle has a perimeter of $\frac{14}{9}P$ meters. What is the value of $P$?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The hypotenuse of an isosceles right triangle has a length of $12$ units. What is the area of the triangle, in square units?

\choicebox{A}{$18\sqrt{2}$}  
\choicebox{B}{$36$}  
\choicebox{C}{$48$}  
\choicebox{D}{$36\sqrt{2}$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In triangles $LMN$ and $RST$, angles $L$ and $R$ each have measure $127^\circ$. Which additional piece of information is sufficient to determine whether triangle $LMN$ is similar to triangle $RST$?

\choicebox{A}{The measures of angles $N$ and $T$.}  
\choicebox{B}{The lengths of sides $LM$ and $RS$.}  
\choicebox{C}{The measures of angles $S$ and $T$.}  
\choicebox{D}{The lengths of sides $MN$ and $ST$.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In triangles $LMN$ and $PQR$, angles $M$ and $Q$ each have measure $54^\circ$, $MN = 16$, and $QR = 16$. Which additional piece of information is sufficient to prove that triangle $LMN$ is congruent to triangle $PQR$?

\choicebox{A}{Angles $L$ and $R$ each have measure $44^\circ$.}  
\choicebox{B}{Angles $N$ and $P$ each have measure $44^\circ$.}  
\choicebox{C}{$LM = 11$ and $PQ = 11$.}  
\choicebox{D}{$LN = 11$ and $PR = 11$.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In triangles $LMN$ and $PQR$, angles $M$ and $Q$ each have measure $54^\circ$, $MN = 16$, and $QR = 16$. Which additional piece of information is sufficient to prove that triangle $LMN$ is congruent to triangle $PQR$?

\choicebox{A}{Angles $L$ and $R$ each have measure $44^\circ$.}  
\choicebox{B}{Angles $N$ and $P$ each have measure $44^\circ$.}  
\choicebox{C}{$LM = 11$ and $PQ = 11$.}  
\choicebox{D}{$LN = 11$ and $PR = 11$.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In triangle $ABC$, the measure of angle $A$ is $25^\circ$, angle $C$ is a right angle, and the length of $BC$ is $16$. Which of the following represents the length of $AC$?

\choicebox{A}{$16 \sin 25^\circ$}  
\choicebox{B}{$16 \tan 25^\circ$}  
\choicebox{C}{$\frac{16}{\sin 25^\circ}$}  
\choicebox{D}{$\frac{16}{\tan 25^\circ}$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Triangle $JKL$ is similar to triangle $RST$, where angle $J$ corresponds to angle $R$ and angles $K$ and $S$ are right angles. If $\cos(L) = \frac{119}{169}$, what is the value of $\tan(T)$?

\choicebox{A}{$\frac{120}{169}$}  
\choicebox{B}{$\frac{119}{120}$}  
\choicebox{C}{$\frac{120}{119}$}  
\choicebox{D}{$\frac{169}{119}$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Point $O$ is the center of a circle. The measure of arc $MN$ on this circle is $\frac{4\pi}{3}$ radians. The length of arc $MN$ is what fraction of the circumference of the circle?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, segment $OA$ has endpoints $(0,0)$ and $(\sqrt{3}, \sqrt{3})$. What is the measure, in radians, of the acute angle formed by segment $OA$ and the line $y = 0$?

\choicebox{A}{$\frac{\pi}{6}$}  
\choicebox{B}{$\frac{\pi}{4}$}  
\choicebox{C}{$\frac{\pi}{3}$}  
\choicebox{D}{$\frac{\pi}{2}$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Triangle $ABC$ is similar to triangle $DEF$, where angle $A$ corresponds to angle $D$ and angles $B$ and $E$ are right angles. If $AB = 2$, $DF = 12\sqrt{2}$, and $\tan(A) = \sqrt{7}$, what is the length of $DE$?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, circle $A$ is defined by the equation $(x - 3)^2 + (y - 4)^2 = 16$, and circle $B$ is defined by the equation $(x - 3)^2 + (y - 4)^2 = n$, where $n$ is a constant. The diameter of circle $B$ is $48$ units longer than the diameter of circle $A$. What is the value of $n$?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The given equation represents a circle in the $xy$-plane:
\[
x^2 + y^2 + 7x + y = -\frac{7}{2}
\]
What is the length of the radius of the circle?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, a circle has center $D$ with coordinates $(m,16)$, where $m$ is a constant. Points $E$ and $F$ lie on the circle. Point $E$ lies on the circle and has coordinates $\bigl(m + 4\sqrt{10}, 34\bigr)$, and point $F$ has coordinates $(n,16)$, where $n$ is a constant greater than $m$. What is the area, in square units, of triangle $DEF$?

\choicebox{A}{$198$}  
\choicebox{B}{$72\sqrt{10}$}  
\choicebox{C}{$242$}  
\choicebox{D}{$99\sqrt{10}$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, a circle has center $D$ with coordinates $(m,16)$, where $m$ is a constant. Points $E$ and $F$ lie on the circle. Point $E$ lies on the circle and has coordinates $\bigl(m + 4\sqrt{10}, 34\bigr)$, and point $F$ has coordinates $(n,16)$, where $n$ is a constant greater than $m$. What is the area, in square units, of triangle $DEF$?

\choicebox{A}{$198$}  
\choicebox{B}{$72\sqrt{10}$}  
\choicebox{C}{$242$}  
\choicebox{D}{$99\sqrt{10}$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A circle in the $xy$-plane has the equation:
\[
(x - 2)^2 + (y - 2)^2 = 25.
\]
Line $m$ is tangent to this circle at the point $(5,6)$. What is the $y$-coordinate of the $y$-intercept of line $m$?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

If $\theta = 3x + 4$, and $\beta = 6x - 5$, what is the value of $x$ so that $\sin(\theta) = \cos(\beta)$?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A circle has center $O$, and points $M$ and $N$ lie on the circle. The measure of arc $MN$ is $24^\circ$ and the length of arc $MN$ is $8\pi$ centimeters. What is the length, in centimeters, of the radius of the circle?

\choicebox{A}{$15$}  
\choicebox{B}{$45$}  
\choicebox{C}{$60$}  
\choicebox{D}{$120$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Which of the following equations represents a circle in the $xy$-plane that intersects the line $x = 5$ at exactly one point?

\choicebox{A}{$(x - 1)^2 + (y - 7)^2 = 4$}  
\choicebox{B}{$(x - 5)^2 + (y - 1)^2 = 4$}  
\choicebox{C}{$(x - 7)^2 + (y - 5)^2 = 4$}  
\choicebox{D}{$(x - 13)^2 + (y - 13)^2 = 4$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A circle has center $A$, and points $B$ and $C$ lie on the circle. Line segment $BD$ is tangent to the circle at point $B$, line segment $CD$ is tangent to the circle at point $C$, and the length of line segment $BD$ is $63$ units. If the circle has a radius of $16$ units, what is the area, in square units, of quadrilateral $ABCD$?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, a circle with a radius of $1$ has its center at $(9, -12)$. This circle can be represented by the equation $x^2 + y^2 + ax + by + c = 0$, where $a$, $b$, and $c$ are constants. What is the value of $a + b + c$?
