\documentclass{beamer}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{amsmath}

\definecolor{purpleblue}{RGB}{80, 80, 180}
\definecolor{novelPurple}{RGB}{98, 54, 255}
\definecolor{softPurple}{RGB}{180, 170, 255}
\definecolor{softGray}{RGB}{235, 235, 245}
\definecolor{lightText}{RGB}{90, 90, 110}

\usetheme{Madrid}
\usecolortheme{dolphin}
\graphicspath{{static/course_materials/}{static/hard/}{./}}

\setbeamerfont{title}{size=\Large,series=\bfseries}
\setbeamerfont{frametitle}{size=\LARGE,series=\bfseries}
\setbeamercolor{frametitle}{fg=white, bg=novelPurple}
\setbeamercolor{title}{fg=white, bg=purpleblue}

\title[SAT Hard Question 16]{\textbf{SAT Hard Question\\ Set 16}}
\author{\textbf{Jack Zeng}}
\institute{\textcolor{white}{\textbf{Novel Prep}}}
\date{\today}

\begin{document}

\begin{frame}
    \titlepage
    \vfill
    \begin{flushright}
        \textcolor{purpleblue}{\Huge \textbf{Novel Prep}}
    \end{flushright}
\end{frame}

\begin{frame}
    \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=softPurple, bottom color=softGray]
            (current page.north west) rectangle (current page.south east);
        \node[align=center] at (current page.center) {
            {\Huge\bfseries\textcolor{purpleblue}{Novel Prep}} \\[0.5cm]
            {\Large\itshape\textcolor{lightText}{Phase 2 · Hard Question Practice}}
        };
    \end{tikzpicture}
\end{frame}

\begin{frame}{Overview}
    \tableofcontents
\end{frame}

\begin{frame}
\section{Hard Question Set 16}
    \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=softPurple, bottom color=softGray]
            (current page.north west) rectangle (current page.south east);
        \node[align=center] at (current page.center) {
            {\LARGE\bfseries\textcolor{purpleblue}{Hard Question Set 16}} \\[0.5cm]
            {\Large\itshape\textcolor{lightText}{13 SAT-style challenge problems}}
        };
    \end{tikzpicture}
\end{frame}

% --- Question 1 ---
\begin{frame}{Question 1}
\small
The function \(h\) is defined as:
\[
h(t) = -16t^2 + b
\]
The function \(h\) estimates an object's height, in feet, above the ground \(t\) seconds after the object is dropped, where \(b\) is a constant.

The function estimates that the object is \(40.96\) feet above the ground when it is dropped at \(t = 0\).

How many seconds after being dropped does the function estimate the object will hit the ground?
\end{frame}
\begin{frame}{Answer 1}
\small
\textbf{Final Answer:} $\boxed{1.6}$
\end{frame}

% --- Question 2 ---
\begin{frame}{Question 2}
\small
For a set of three consecutive integers, the result of subtracting the greatest integer from the sum of the other two integers is \(48\).

What is the value of the greatest of the three integers?
\end{frame}
\begin{frame}{Answer 2}
\small
\textbf{Final Answer:} $\boxed{51}$
\end{frame}

% --- Question 3 ---
\begin{frame}{Question 3}
\small
A researcher surveyed undergraduate students, graduate students, and postdoctoral students. The number of undergraduate students surveyed was \(7{,}150\%\) of the number of postdoctoral students surveyed, and the number of graduate students surveyed was \(45\%\) of the number of undergraduate students surveyed.

If there were \(6{,}435\) graduate students surveyed, what was the sum of the number of undergraduate students and postdoctoral students surveyed?
\end{frame}
\begin{frame}{Answer 3}
\small
\textbf{Final Answer:} $\boxed{14500}$
\end{frame}

% --- Question 4 ---
\begin{frame}{Question 4}
\small
\[
\begin{aligned}
16x - 20y &= 6y + 8 \\
ty &= 8x + \frac{1}{5}
\end{aligned}
\]

In the given system of equations, \(t\) is a constant. If the system has no solution, what is the value of \(t\)?
\end{frame}
\begin{frame}{Answer 4}
\small
\textbf{Final Answer:} $\boxed{13}$
\end{frame}

% --- Question 5 ---
\begin{frame}{Question 5}
\small
The bone mineral density of a certain person's thoracic spine was estimated to be \(0.812\) grams per square centimeter. What is this estimated bone mineral density in grams per square millimeter? (\(1\) centimeter \(= 10\) millimeters)
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \(81.2\)
    \item[B.] \(8.12\)
    \item[C.] \(0.0812\)
    \item[D.] \(0.00812\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 5}
\small
\textbf{Correct Answer:} D
\end{frame}

% --- Question 6 ---
\begin{frame}{Question 6}
\small
\[
\frac{5}{9}(5x + 9)\left(x + \sqrt{5k + 9}\right)\left(x - \sqrt{5k + 9}\right) = 0
\]

In the given equation, \(k\) is a positive constant. The product of the solutions to the equation is \(72\).

What is the value of \(k\)?
\end{frame}
\begin{frame}{Answer 6}
\small
\textbf{Final Answer:} $\boxed{6.2}$
\end{frame}

% --- Question 7 ---
\begin{frame}{Question 7}
\small
A right rectangular prism has a base area of \(56t\) square centimeters (\(\text{cm}^2\)). The length of the base of the rectangular prism is \(\frac{14}{3}\) cm, and the height of the rectangular prism is \(3\) cm.

Which expression represents the surface area, in \(\text{cm}^2\), of the right rectangular prism?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \(112t + 56\)
    \item[B.] \(184t + 28\)
    \item[C.] \(1{,}680t + 28\)
    \item[D.] \(168t\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 7}
\small
\textbf{Correct Answer:} B
\end{frame}

% --- Question 8 ---
\begin{frame}{Question 8}
\small
In the \(xy\)-plane, a unit circle with center at the origin \(O\) contains point \(A\) with coordinates \((1, 0)\) and point \(B\) with coordinates \(\left(\frac{5}{\sqrt{34}}, -\frac{3}{\sqrt{34}}\right)\).

If the measure of angle \(AOB\) is \(p\) radians, what is the value of \(\frac{\cos p}{\sin p}\)?
\end{frame}
\begin{frame}{Answer 8}
\small
\textbf{Final Answer:} $\boxed{\dfrac{-5}{3}}$
\end{frame}

% --- Question 9 ---
\begin{frame}{Question 9}
\small
The function \(h\) is defined by
\[
h(x) = -\sqrt{x^2 + bx + c},
\]
where \(b\) and \(c\) are constants. In the \(xy\)-plane, the graph of \(y = h(x)\) contains the points \((2, 0)\) and \(\left(0, -\sqrt{334}\right)\).

If \(h(m) = 0\), what is the greatest possible value of \(m\)?
\end{frame}
\begin{frame}{Answer 9}
\small
\textbf{Final Answer:} $\boxed{167}$
\end{frame}

% --- Question 10 ---
\begin{frame}{Question 10}
\small
A computer repair specialist charges \(\$160\) for the first two hours of repair plus an hourly fee for each additional hour. The total cost for \(6\) hours of repair is \(\$360\).

Which function \(f\) gives the total cost, in dollars, for \(x\) hours of repair, where \(x \geq 2\)?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \(f(x) = 50x + 60\)
    \item[B.] \(f(x) = 50x + 160\)
    \item[C.] \(f(x) = 60x\)
    \item[D.] \(f(x) = 60x + 160\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 10}
\small
\textbf{Correct Answer:} A
\end{frame}

% --- Question 11 ---
\begin{frame}{Question 11}
\small
A painting studio is offering a promotion where the first class is free, the second class is half off the regular price, and the remaining classes are regularly priced. If the regular price of a class is \(\$26.40\), which function \(f\) gives the total cost, in dollars, of \(x\) classes taken using this promotion, where \(x > 2\)?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \(f(x) = 26.40(x - 1) + 13.20\)
    \item[B.] \(f(x) = 26.40(x - 2) + 13.20\)
    \item[C.] \(f(x) = 26.40(x - 1) + 13.20(x - 2)\)
    \item[D.] \(f(x) = 26.40(x - 2) + 13.20(x - 1)\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 11}
\small
\textbf{Correct Answer:} B
\end{frame}

% --- Question 12 ---
\begin{frame}{Question 12}
\small
The function \(f\) is defined by the given equation:
\[
f(x) = x^2 - 4x - 320
\]
Which of the following equivalent forms of the equation displays the minimum value of the function as a constant or coefficient?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \(f(x) = x^2 - 4(x + 80)\)
    \item[B.] \(f(x) = (x - 2)^2 + (-324)\)
    \item[C.] \(f(x) = x(x - 4) + (-320)\)
    \item[D.] \(f(x) = (x + 16)(x - 20)\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 12}
\small
\textbf{Correct Answer:} B
\end{frame}

% --- Question 13 ---
\begin{frame}{Question 13}
\small
The composition of an animal is defined as the muscles, bones, and fat of the animal. A scientist studied the composition of one young swamp buffalo and determined the buffalo had \(133\) kilograms of muscle, which made up approximately \(65.9\%\) of its composition. Of the remaining composition of this buffalo, approximately \(46.2\%\) was bone, and the remainder was fat. Based on these approximations, to the nearest tenth, how many kilograms of this buffalo's composition was bone?
\end{frame}
\begin{frame}{Answer 13}
\small
\textbf{Final Answer:} $\boxed{31.8}$
\end{frame}

\begin{frame}{}
    \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=novelPurple!40, bottom color=white]
            (current page.north west) rectangle (current page.south east);
        \fill[white, opacity=0.15] (current page.center) circle (5cm);
        \foreach \x in {1,2,3,4,5} {
            \fill[novelPurple, opacity=0.12] (rand*10-5, rand*7-3.5) circle (0.1+\x*0.05);
        }
    \end{tikzpicture}
    \centering
    \vspace{5em}
    {\Huge \textbf{\textcolor{novelPurple}{Thank You!}}} \\[1em]
    {\large \textcolor{gray}{We appreciate your time and focus.}} \\[3em]
    {\LARGE \textbf{\textcolor{novelPurple}{\textsf{Novel Prep}}}}
    \vfill
\end{frame}

\end{document}
