\documentclass{beamer}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{amsmath}

% 自定义颜色
\definecolor{purpleblue}{RGB}{80, 80, 180}
\definecolor{lightgray}{RGB}{230, 230, 230}
\definecolor{novelPurple}{RGB}{98, 54, 255}
\definecolor{darkgray}{RGB}{50, 50, 50}
\definecolor{softPurple}{RGB}{180, 170, 255}
\definecolor{softGray}{RGB}{235, 235, 245}
\definecolor{lightText}{RGB}{90, 90, 110}
\graphicspath{{static/course_materials/}{./}}

% 主题设置
\usetheme{Madrid}
\usecolortheme{dolphin}

\setbeamerfont{title}{size=\Large,series=\bfseries}
\setbeamerfont{frametitle}{size=\LARGE,series=\bfseries}
\setbeamercolor{frametitle}{fg=white, bg=novelPurple}
\setbeamercolor{title}{fg=white, bg=purpleblue}

\title[SAT Unit 3.5]{\textbf{SAT Unit 3.5 \\Probability}}
\author{\textbf{Jack Zeng}}
\institute{\textcolor{white}{\textbf{Novel Prep}}}
\date{\today}

\begin{document}


% --- Title Slide ---
\begin{frame}
    \titlepage
    \vfill
    \begin{flushright}
        \textcolor{purpleblue}{\Huge \textbf{Novel Prep}}
    \end{flushright}
\end{frame}

\begin{frame}
    \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=softPurple, bottom color=softGray]
            (current page.north west) rectangle (current page.south east);
        \fill[white, opacity=0.3] (current page.center) circle (4cm);
        \node[align=center] at (current page.center) {
            {\Huge\bfseries\textcolor{purpleblue}{Novel Prep}} \\[0.5cm]
            {\Large\itshape\textcolor{lightText}{Excellence in SAT Prep}}
        };
        \foreach \x in {1,2,3,4,5} {
            \fill[purpleblue, opacity=0.2] (rand*10-5, rand*7-3.5) circle (0.1+\x*0.05);
        }
    \end{tikzpicture}
\end{frame}

\begin{frame}{Overview}
    \tableofcontents
\end{frame}

\begin{frame}
\section{Probability}
    \begin{tikzpicture}[remember picture, overlay]
        % 设置浅色渐变背景
        \shade[top color=softPurple, bottom color=softGray] 
            (current page.north west) rectangle (current page.south east);
        
        % 添加高斯模糊光晕
        \fill[white, opacity=0.3] (current page.center) circle (4cm);
        
        % 主标题
        \node[align=center] at (current page.center) {
            {\LARGE\bfseries\textcolor{purpleblue}{ Probability}} \\[0.5cm]
            {\Large\itshape\textcolor{lightText}{Excellence in SAT Prep}}
        };

        % 添加柔和光点（点缀）
        \foreach \x in {1,2,3,4,5} {
            \fill[purpleblue, opacity=0.2] (rand*10-5, rand*7-3.5) circle (0.1+\x*0.05);
        }

        ;
    \end{tikzpicture}
\end{frame}


\begin{frame}{Definition of Probability}
    
\textbf{Probability} is a measure of how likely an event is to occur. It is defined as:

\[
P(\text{Event}) = \frac{\text{Number of favorable outcomes}}{\text{Total number of possible outcomes}}
\]

\textbf{Key Properties:}
\begin{itemize}
    \item \(0 \leq P(A) \leq 1\) for any event \(A\)
    \item \(P(\text{certain event}) = 1\)
    \item \(P(\text{impossible event}) = 0\)
    \item \(P(\text{not A}) = 1 - P(A)\)
    \item For mutually exclusive events \(A\) and \(B\):
    \[
    P(A \text{ or } B) = P(A) + P(B)
    \]
\end{itemize}

\end{frame}

\begin{frame}{Simple Probability Examples}
    
\textbf{Example 1:} A fair die is rolled. What is the probability of getting an even number?

\[
\text{Even numbers: } \{2, 4, 6\} \Rightarrow \text{Favorable outcomes: } 3
\]
\[
\text{Total outcomes: } 6 \Rightarrow P(\text{even}) = \frac{3}{6} = \frac{1}{2}
\]

\vspace{0.3cm}
\textbf{Example 2:} A card is drawn from a standard deck. What is the probability of drawing a heart?

\[
\text{Hearts: } 13,\quad \text{Total cards: } 52 \Rightarrow P(\text{heart}) = \frac{13}{52} = \frac{1}{4}
\]

\end{frame}


\begin{frame}{Conditional Probability (Concept)}
    
\textbf{Conditional Probability} is the probability of event \(A\) occurring \textbf{given} that event \(B\) has occurred.

\[
P(A \mid B) = \frac{P(A \cap B)}{P(B)}
\]

\textbf{Key Points:}
\begin{itemize}
    \item \(P(A \mid B)\) narrows the sample space to only outcomes where \(B\) happens.
    \item Only defined if \(P(B) \ne 0\).
\end{itemize}

\textbf{Visual:}

Think of "restricting" the universe to \(B\), and checking how many of those are also \(A\)


\end{frame}

\begin{frame}{\textbf{Question: Probability - Score Distribution Table}}

The same 20 contestants, on each of 3 days, answered 5 questions in order to win a prize. Each contestant received 1 point for each correct answer. The number of contestants receiving a given score on each day is shown in the table below.

\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
\textbf{Score} & \textbf{Day 1} & \textbf{Day 2} & \textbf{Day 3} & \textbf{Total} \\
\hline
5 out of 5 & 2 & 2 & 3 & 7 \\
4 out of 5 & 3 & 3 & 3 & 9 \\
3 out of 5 & 4 & 5 & 3 & 13 \\
2 out of 5 & 6 & 5 & 4 & 15 \\
1 out of 5 & 2 & 4 & 3 & 9 \\
0 out of 5 & 3 & 1 & 2 & 6 \\
\hline
\textbf{Total} & 20 & 20 & 20 & 60 \\
\hline
\end{tabular}
\end{center}

No contestant received the same score on two different days. If a contestant is selected at random, what is the probability that the selected contestant received a score of 5 on Day 2 or Day 3, given that the contestant received a score of 5 on one of the three days?

\end{frame}

\begin{frame}{\textbf{Answer Explanation: Probability - Score Distribution Table}}
    
\textbf{Problem Context:}
\begin{itemize}
    \item 20 contestants each day, over 3 days (no repeat scores).
    \item Table shows number of contestants scoring 0–5 on each day.
    \item Total scores of 5 across all days: \(2 + 2 + 3 = 7\)
\end{itemize}


\textbf{Given:} A contestant received a score of \(5\) on \textbf{one of the days}.

\textbf{Find:} Probability that this contestant scored \(5\) on Day 2 or Day 3.


\textbf{Step 1: Count favorable outcomes}
\[
\text{Day 2: } 2 \qquad \text{Day 3: } 3 \qquad \text{Total favorable} = 2 + 3 = 5
\]

\vspace{0.1cm}
\textbf{Step 2: Count total outcomes}
\[
\text{Total contestants with score of 5: } 7
\]

\vspace{0.1cm}
\textbf{Answer:}
\[
P(\text{Day 2 or Day 3} \mid \text{Score 5}) = \frac{5}{7}
\]

\textbf{Correct Answer:} \( \boxed{\frac{5}{7}} \)

\end{frame}



\begin{frame}
\section{Practice}
    \begin{tikzpicture}[remember picture, overlay]
        % 设置浅色渐变背景
        \shade[top color=softPurple, bottom color=softGray] 
            (current page.north west) rectangle (current page.south east);
        
        % 添加高斯模糊光晕
        \fill[white, opacity=0.3] (current page.center) circle (4cm);
        
        % 主标题
        \node[align=center] at (current page.center) {
            {\Huge\bfseries\textcolor{purpleblue}{Practice}} \\[0.5cm]
            {\Large\itshape\textcolor{lightText}{Excellence in SAT Prep}}
        };

        % 添加柔和光点（点缀）
        \foreach \x in {1,2,3,4,5} {
            \fill[purpleblue, opacity=0.2] (rand*10-5, rand*7-3.5) circle (0.1+\x*0.05);
        }

        ;
    \end{tikzpicture}
\end{frame}


\begin{frame}{\textbf{Question: The table summarizes the distribution of age and…}}
The table summarizes the distribution of age and favorite sport for 150 members of a country club.

\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
 & Squash & Tennis & Golf & Total \\
\hline
30–44 years & 18 & 10 & 22 & 50 \\
45–59 years & 11 & 14 & 25 & 50 \\
60+ years & 21 & 26 & 3 & 50 \\
\hline
Total & 50 & 50 & 50 & 150 \\
\hline
\end{tabular}
\end{center}

One of these members will be selected at random. What is the probability of selecting a member whose favorite sport is tennis, given that the member is at least 45 years of age? (Express your answer as a decimal or fraction, not as a percent.)
\end{frame}
\begin{frame}{\textbf{Answer Explanation: The table summarizes the distribution of age and…}}
\textbf{Step 1. Identify the relevant group:}
\[
\text{At least 45 years of age} = (45–59) + (60+) = 50 + 50 = 100.
\]

\textbf{Step 2. Find the total number of tennis players in that group:}
\[
14 (\text{45–59}) + 26 (\text{60+}) = 40.
\]

\textbf{Step 3. Calculate the probability:}
\[
P(\text{Tennis} \mid \text{At least 45}) = \frac{40}{100} = 0.4.
\]

\textbf{Answer:} \(\boxed{0.4}\).
\end{frame}


\begin{frame}{\textbf{Question: A new medical test is designed to give a positive…}}
A new medical test is designed to give a positive indicator to a patient who has a certain virus and a negative indicator to a patient who does not. The table summarizes the results for 1,000 patients who have taken this test.

\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
 & Negative Indicator & Positive Indicator & Total \\
\hline
Has virus & 30 & 370 & 400 \\
Does not have virus & 550 & 50 & 600 \\
\hline
Total & 580 & 420 & 1,000 \\
\hline
\end{tabular}
\end{center}

Based on the table, what is the probability that the test gives the wrong indicator?

\begin{itemize}
 \item[\textbf{A.}] 5\%
 \item[\textbf{B.}] 8\%
 \item[\textbf{C.}] 10\%
 \item[\textbf{D.}] 12\%
\end{itemize}
\end{frame}


\begin{frame}{\textbf{Answer Explanation: A new medical test is designed to give a positive…}}
\textbf{Step 1. Count the number of wrong indicators:}
\begin{itemize}
    \item False negatives (Has virus, but test negative): 30
    \item False positives (Does not have virus, but test positive): 50
\end{itemize}
\[
30 + 50 = 80
\]

\textbf{Step 2. Divide by the total number of patients:}
\[
\frac{80}{1,000} = 0.08
\]

\textbf{Step 3. Answer:}
\[
0.08 = 8\%
\]

\textbf{Correct Answer:} \( \boxed{B} \)
\end{frame}


\begin{frame}{\textbf{Question: The table shows the results of a survey in which…}}
The table shows the results of a survey in which students at three colleges were asked whether they live on campus or off campus.

\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
 & Off campus & On campus & Total \\
\hline
College A & 335 & 689 & 1,024 \\
College B & 124 & 482 & 606 \\
College C & 596 & 274 & 870 \\
\hline
Total & 1,055 & 1,445 & 2,500 \\
\hline
\end{tabular}
\end{center}

If one of the students surveyed is selected at random, which of the following probabilities has the greatest value?

\begin{itemize}
 \item[\textbf{A.}] The probability that the student lives off campus, given that the student attends College C.
 \item[\textbf{B.}] The probability that the student lives on campus, given that the student attends College C.
 \item[\textbf{C.}] The probability that the student attends College C, given that the student lives off campus.
 \item[\textbf{D.}] The probability that the student attends College C, given that the student lives on campus.
\end{itemize}
\end{frame}


\begin{frame}{\textbf{Answer Explanation: The table shows the results of a survey in which…}}
\textbf{Step 1. Calculate each conditional probability:}

\begin{itemize}
    \item A: \(\frac{596}{870} \approx 0.685\)
    \item B: \(\frac{274}{870} \approx 0.315\)
    \item C: \(\frac{596}{1055} \approx 0.565\)
    \item D: \(\frac{274}{1445} \approx 0.19\)
\end{itemize}

\textbf{Step 2. Compare:}
\[
0.685 > 0.565 > 0.315 > 0.19
\]

\textbf{Correct Answer:} \( \boxed{A} \)
\end{frame}

\begin{frame}{}
    \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=novelPurple!40, bottom color=white]
            (current page.north west) rectangle (current page.south east);
        \fill[white, opacity=0.15] (current page.center) circle (5cm);
        \foreach \x in {1,2,3,4,5} {
            \fill[novelPurple, opacity=0.12] (rand*10-5, rand*7-3.5) circle (0.1+\x*0.05);
        }
    \end{tikzpicture}
    \centering
    \vspace{5em}
    {\Huge \textbf{\textcolor{novelPurple}{Thank You!}}} \\[1em]
    {\large \textcolor{gray}{We appreciate your time and focus.}} \\[3em]
    {\LARGE \textbf{\textcolor{novelPurple}{\textsf{Novel Prep}}}}
    \vfill
\end{frame}

\end{document}
