\documentclass{beamer}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{amsmath}

\definecolor{purpleblue}{RGB}{80, 80, 180}
\definecolor{novelPurple}{RGB}{98, 54, 255}
\definecolor{softPurple}{RGB}{180, 170, 255}
\definecolor{softGray}{RGB}{235, 235, 245}
\definecolor{lightText}{RGB}{90, 90, 110}

\usetheme{Madrid}
\usecolortheme{dolphin}
\graphicspath{{static/course_materials/}{static/hard/}{./}}

\setbeamerfont{title}{size=\Large,series=\bfseries}
\setbeamerfont{frametitle}{size=\LARGE,series=\bfseries}
\setbeamercolor{frametitle}{fg=white, bg=novelPurple}
\setbeamercolor{title}{fg=white, bg=purpleblue}

\title[SAT Hard Question 13]{\textbf{SAT Hard Question\\ Set 13}}
\author{\textbf{Jack Zeng}}
\institute{\textcolor{white}{\textbf{Novel Prep}}}
\date{\today}

\begin{document}

\begin{frame}
    \titlepage
    \vfill
    \begin{flushright}
        \textcolor{purpleblue}{\Huge \textbf{Novel Prep}}
    \end{flushright}
\end{frame}

\begin{frame}
    \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=softPurple, bottom color=softGray]
            (current page.north west) rectangle (current page.south east);
        \node[align=center] at (current page.center) {
            {\Huge\bfseries\textcolor{purpleblue}{Novel Prep}} \\[0.5cm]
            {\Large\itshape\textcolor{lightText}{Phase 2 · Hard Question Practice}}
        };
    \end{tikzpicture}
\end{frame}

\begin{frame}{Overview}
    \tableofcontents
\end{frame}

\begin{frame}
\section{Hard Question Set 13}
    \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=softPurple, bottom color=softGray]
            (current page.north west) rectangle (current page.south east);
        \node[align=center] at (current page.center) {
            {\LARGE\bfseries\textcolor{purpleblue}{Hard Question Set 13}} \\[0.5cm]
            {\Large\itshape\textcolor{lightText}{13 SAT-style challenge problems}}
        };
    \end{tikzpicture}
\end{frame}

% --- Question 1 ---
\begin{frame}{Question 1}
\small
A circle has center \(O\), and points \(A\) and \(B\) lie on the circle.
The measure of arc \(AB\) is \(60^\circ\), and the length of this arc is 4 inches.
What is the circumference, in inches, of the circle?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] 4
    \item[B.] 8
    \item[C.] 16
    \item[D.] 24
\end{enumerate}
\end{frame}
\begin{frame}{Answer 1}
\small
\textbf{Correct Answer:} D
\end{frame}

% --- Question 2 ---
\begin{frame}{Question 2}
\small
In the \(xy\)-plane, the graph of function \(f\), where \(y = f(x)\), has exactly 8 \(x\)-intercepts.
One of these \(x\)-intercepts is \((17, 0)\).
The rational function \(g\) is defined by:
\[
g(x) = \frac{f(x)}{x - 17}
\]
In the \(xy\)-plane, how many \(x\)-intercepts does the graph of \(y = g(x)\) have?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] 5
    \item[B.] 6
    \item[C.] 7
    \item[D.] 8
\end{enumerate}
\end{frame}
\begin{frame}{Answer 2}
\small
\textbf{Correct Answer:} C
\end{frame}

% --- Question 3 ---
\begin{frame}{Question 3}
\small
A researcher investigated two species of mites: a predator and its prey.
At the start of a week, there was an equal number of the two species.
At the end of the week:

\begin{itemize}
\item The number of prey had increased by 2700\% of the number of prey at the start of the week.
\item The number of predators had increased by 180\% of the number of predators at the start of the week.
\end{itemize}

The number of prey at the end of the week was \(p\%\) greater than the number of predators at the end of the week.
What is the value of \(p\)?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] 9
    \item[B.] 90
    \item[C.] 900
    \item[D.] 9000
\end{enumerate}
\end{frame}
\begin{frame}{Answer 3}
\small
\textbf{Correct Answer:} C
\end{frame}

% --- Question 4 ---
\begin{frame}{Question 4}
\small
The exponential function \(f\) is defined by
\[
f(x) = ab^x,
\]
where \(a\) and \(b\) are positive constants.
If \(f(s) = t\) and \(f(s + 1) = t - 0.87t\), where \(s\) and \(t\) are constants, what is the value of \(b\)?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] 0.13
    \item[B.] 0.87
    \item[C.] 1.13
    \item[D.] 1.87
\end{enumerate}
\end{frame}
\begin{frame}{Answer 4}
\small
\textbf{Correct Answer:} A
\end{frame}

% --- Question 5 ---
\begin{frame}{Question 5}
\small
A beekeeper's initial observation of the population of a certain bee colony was 1,100 bees.
The beekeeper set a goal to increase the population to 2,600 bees.

The beekeeper uses a model that predicts the population of this bee colony:

\begin{itemize}
\item begins at 1,100
\item increases by 120 bees per week in the first two weeks
\item then increases by 180 bees per week until the goal is reached
\end{itemize}

According to this model, at the end of week \(w\) after the initial observation, where \(w > 2\),
which of the following functions gives the predicted number of bees still needed to reach the beekeeper's goal?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \(p(w) = 2600 - 180w\)
    \item[B.] \(p(w) = 2480 + 180w\)
    \item[C.] \(p(w) = 1620 - 180w\)
    \item[D.] \(p(w) = -120 + 180w\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 5}
\small
\textbf{Correct Answer:} C
\end{frame}

% --- Question 6 ---
\begin{frame}{Question 6}
\small
Given the quadratic equation:
\[
7rx^2 - 28sx + 7r = 0
\]
In the equation:

\begin{itemize}
\item \(r\) is a positive constant
\item \(s\) is a negative constant
\item The equation has two solutions
\end{itemize}

If \(\frac{r}{s} > k\), what is the minimum value of \(k\)?
\end{frame}
\begin{frame}{Answer 6}
\small
\textbf{Final Answer:} $\boxed{-2}$
\end{frame}

% --- Question 7 ---
\begin{frame}{Question 7}
\small
A square map has a side length of 55 inches, and 1 inch on the map represents an actual distance of 13 miles.
A larger version of the same map is printed as a square with the side length 90\% longer than the side length of the previous map.
On the larger map, which of the following is closest to the actual distance, in miles, represented by 1 inch?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] 1.30
    \item[B.] 6.84
    \item[C.] 24.70
    \item[D.] 49.50
\end{enumerate}
\end{frame}
\begin{frame}{Answer 7}
\small
\textbf{Correct Answer:} B
\end{frame}

% --- Question 8 ---
\begin{frame}{Question 8}
\small
In isosceles triangle \(ABC\), sides \(AB\) and \(AC\) are congruent.
Point \(D\) divides side \(\overline{BC}\) such that the length of \(\overline{BD}\) is \(\frac{4}{7}\) of the length of \(\overline{BC}\).
Point \(E\) lies on side \(AB\) and point \(F\) lies on side \(AC\) such that when segments \(\overline{DE}\) and \(\overline{DF}\) are drawn, \(\angle BED\) is congruent to \(\angle CFD\).
If the length of \(\overline{BE}\) is 8, what is the length of \(\overline{CF}\)?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] 6
    \item[B.] 14
    \item[C.] 32
    \item[D.] 56
\end{enumerate}
\end{frame}
\begin{frame}{Answer 8}
\small
\textbf{Correct Answer:} A
\end{frame}

% --- Question 9 ---
\begin{frame}{Question 9}
\small
\[
\frac{\sqrt[3]{x^{17}y^5}}{5x^2\left(\sqrt[8]{y^8}\right)}
\]

For all positive values of \(x\) and \(y\), the given expression is equivalent to which of the following?

\begin{itemize}
\item[I] \(\dfrac{x^{\frac{14}{3}}y^{\frac{5}{3}}}{5xy}\)
\item[II] \(\dfrac{\sqrt[3]{x^{11}y^2}}{5}\)
\end{itemize}
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] I only
    \item[B.] II only
    \item[C.] I and II
    \item[D.] Neither I nor II
\end{enumerate}
\end{frame}
\begin{frame}{Answer 9}
\small
\textbf{Correct Answer:} C
\end{frame}

% --- Question 10 ---
\begin{frame}{Question 10}
\small
The table shows three values of \(x\) and their corresponding values of \(y\), where \(s\) is a constant.
There is a linear relationship between \(x\) and \(y\).
Which of the following equations represents this relationship?

\[
\begin{array}{|c|c|}
\hline
x & y \\
\hline
-2s & 24 \\
-s & 21 \\
s & 15 \\
\hline
\end{array}
\]
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \(sx + 3y = 18s\)
    \item[B.] \(3x + sy = 18s\)
    \item[C.] \(3x + sy = 18\)
    \item[D.] \(sx + 3y = 18\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 10}
\small
\textbf{Correct Answer:} B
\end{frame}

% --- Question 11 ---
\begin{frame}{Question 11}
\small
The cost of renting a carpet cleaner is \$52 for the first day and \$26 for each additional day.
Which of the following functions gives the cost \(C(d)\), in dollars, of renting the carpet cleaner for \(d\) days, where \(d\) is a positive integer?
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \(C(d) = 26d + 26\)
    \item[B.] \(C(d) = 26d + 52\)
    \item[C.] \(C(d) = 52d - 26\)
    \item[D.] \(C(d) = 52d + 78\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 11}
\small
\textbf{Correct Answer:} A
\end{frame}

% --- Question 12 ---
\begin{frame}{Question 12}
\small
The speed of a vehicle is increasing at a rate of 7.3 meters per second squared.
What is this rate, in miles per minute squared, rounded to the nearest tenth?
(Use 1 mile = 1,609 meters.)
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] 0.3
    \item[B.] 16.3
    \item[C.] 195.8
    \item[D.] 220.4
\end{enumerate}
\end{frame}
\begin{frame}{Answer 12}
\small
\textbf{Correct Answer:} B
\end{frame}

% --- Question 13 ---
\begin{frame}{Question 13}
\small
The table shows three values of \(x\) and their corresponding values of \(g(x)\), where
\[
g(x) = \frac{f(x)}{x + 5}
\]
and \(f\) is a linear function.
What is the \(y\)-intercept of the graph of \(y = f(x)\) in the \(xy\)-plane?

\[
\begin{array}{|c|c|}
\hline
x & g(x) \\
\hline
-20 & 4 \\
-8 & 0 \\
10 & 6 \\
\hline
\end{array}
\]
\vspace{0.35cm}
\begin{enumerate}
    \item[A.] \((0, -8)\)
    \item[B.] \((0, 5)\)
    \item[C.] \((0, 8)\)
    \item[D.] \((0, 40)\)
\end{enumerate}
\end{frame}
\begin{frame}{Answer 13}
\small
\textbf{Correct Answer:} D
\end{frame}

\begin{frame}{}
    \begin{tikzpicture}[remember picture, overlay]
        \shade[top color=novelPurple!40, bottom color=white]
            (current page.north west) rectangle (current page.south east);
        \fill[white, opacity=0.15] (current page.center) circle (5cm);
        \foreach \x in {1,2,3,4,5} {
            \fill[novelPurple, opacity=0.12] (rand*10-5, rand*7-3.5) circle (0.1+\x*0.05);
        }
    \end{tikzpicture}
    \centering
    \vspace{5em}
    {\Huge \textbf{\textcolor{novelPurple}{Thank You!}}} \\[1em]
    {\large \textcolor{gray}{We appreciate your time and focus.}} \\[3em]
    {\LARGE \textbf{\textcolor{novelPurple}{\textsf{Novel Prep}}}}
    \vfill
\end{frame}

\end{document}
