\subsection*{Unit 1 Practice Test}

\setcounter{questionnum}{0}

\noindent\markforreview
\vspace{1em}

A line in the $xy$-plane is defined by the equation $y = ax + b$, where $a$ and $b$ are constants. The line passes through the points $(0, -79)$ and $(5, 91)$. What is the value of $a + b$?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, the line with equation $ax - \dfrac{1}{3}y = 8$, where $a$ is a constant, passes through the point $(2, 6)$. What is the $x$-coordinate of the $x$-intercept of the line?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The table shows three values of $x$ and their corresponding values of $y$, where $p$ is a constant. There is a linear relationship between $x$ and $y$. What is the slope of the line that represents this relationship in the $xy$-plane?

\vspace{0.5em}

\begin{center}
\begin{tabular}{|c|c|}
\hline
$x$ & $y$ \\
\hline
$-6$ & $-114 - p$ \\
$-2$ & $-57 - p$ \\
$2$ & $-p$ \\
\hline
\end{tabular}
\end{center}

\vspace{0.75em}

\choicebox{A}{$\dfrac{57}{4}$}
\choicebox{B}{$\dfrac{57}{4}$}
\choicebox{C}{$p - \dfrac{57}{4}$}
\choicebox{D}{$2p + \dfrac{57}{4}$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The graph of the equation $5x - 8y = k$, where $k$ is a constant, is a line in the $xy$-plane. The line has an $x$-intercept at $(m, 0)$ and a $y$-intercept at $(0, n)$, where $m$ and $n$ are constants. What is the value of $\dfrac{m}{n}$?

\vspace{0.75em}

\choicebox{A}{$-\dfrac{8}{5}$}
\choicebox{B}{$\dfrac{5}{7}$}
\choicebox{C}{$\dfrac{5}{8}$}
\choicebox{D}{$\dfrac{8}{6}$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, the graph of the linear function $f$ has a negative slope and a $y$-intercept at $(0, k)$, where $k$ is a positive constant. Which of the following must be true?

\vspace{0.5em}

I. If $a > b$, then $f(a) < f(b)$

II. If $a < 0$, then $f(a) > k$

III. If $a > 0$, then $f(a) > 0$

\vspace{0.75em}

\choicebox{A}{I and II only}
\choicebox{B}{I and III only}
\choicebox{C}{II and III only}
\choicebox{D}{I, II, and III}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, the points $(-3, 5)$ and $(6, 8)$ lie on line $\ell$. Which of the following points also lies on line $\ell$?

\vspace{0.75em}

\choicebox{A}{$(27, 15)$}
\choicebox{B}{$(33, 19)$}
\choicebox{C}{$(42, 23)$}
\choicebox{D}{$(54, 27)$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

During a road trip, Carl used 12 gallons of fuel driving a minivan and 17 gallons of fuel driving a campervan. He traveled a total distance of 590 miles driving both vehicles. The equation $12x + 17y = 590$ represents this situation. Which is the best interpretation of $y$ in this context?

\vspace{0.75em}

\choicebox{A}{The total number of gallons of fuel Carl used driving the campervan}
\choicebox{B}{The total number of miles Carl drove the campervan for}
\choicebox{C}{The fuel efficiency, in miles per gallon, of the campervan}
\choicebox{D}{The average fuel efficiency, in miles per gallon, of the minivan and the campervan}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Of the 585 photos in a photo album, 315 are color photos and the rest are black-and-white. The equation $6p + 315 = 585$ describes this situation, where $p$ represents the number of pages that contain black-and-white photos. What is the best interpretation of $6p$ in this context?

\vspace{0.75em}

\choicebox{A}{There are $6p$ black-and-white photos.}
\choicebox{B}{There are $6p$ photos on each page.}
\choicebox{C}{There are $6p$ pages in total.}
\choicebox{D}{There are $6p$ photos in total.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Stacy is playing a game in which she needs to collect a certain number of points to win. The function $p(x) = 52 - 4x$ models the number of additional points Stacy needs to win the game, where $x$ is the number of rounds played. Which of the following is the best interpretation of $p(8) = 20$?

\vspace{0.75em}

\choicebox{A}{Stacy collected a total of 20 points in the first 8 rounds.}
\choicebox{B}{It will take Stacy 8 rounds to collect the 20 additional points she needs to win the game.}
\choicebox{C}{After the first 8 rounds, Stacy needs to collect 20 more points to win the game.}
\choicebox{D}{In the 8th round, Stacy collected 20 more points than she did the previous round.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A party store sells premade banners and custom banners. Yesterday, the store sold a total of 80 banners, earning $x$ dollars in revenue from premade banners and $y$ dollars in revenue from custom banners. The equation $\dfrac{x}{14} + \dfrac{y}{25} = 80$ represents this situation. Which of the following is the best interpretation of 14 in this context?

\vspace{0.75em}

\choicebox{A}{The store sold 14 premade banners yesterday.}
\choicebox{B}{The store earns 14 dollars in revenue for each premade banner sold.}
\choicebox{C}{The store sold 14 custom banners yesterday.}
\choicebox{D}{The store earns 14 dollars in revenue for each custom banner sold.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The given function $h(t) = 100 - 4t$ models the number of hours until a gallon of milk held at a temperature of $t$, in degrees Celsius, goes sour. Which of the following is the best interpretation of the number 4 in this context?

\vspace{0.75em}

\choicebox{A}{An increase of $1^\circ\text{C}$ will make a gallon of milk go sour 4 hours faster.}
\choicebox{B}{An increase of $1^\circ\text{C}$ will make 4 gallons of milk go sour 1 hour faster.}
\choicebox{C}{An increase of $4^\circ\text{C}$ will make a gallon of milk go sour 1 hour faster.}
\choicebox{D}{An increase of $4^\circ\text{C}$ will make a gallon of milk go sour 4 hours faster.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The given function $h(t) = 3.5\left(\dfrac{t}{50} + 2\right)$ models the height of a tree, in inches, $t$ days after it is planted. According to the model, about how many inches does it grow each day?

\vspace{0.75em}

\choicebox{A}{0.02}
\choicebox{B}{0.07}
\choicebox{C}{1.75}
\choicebox{D}{3.5}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The given function $C(x) = 1.5 + 2.5x$ models the cost, in dollars, of mailing a shipment weighing $x$ pounds. According to the model, an increase of 10 dollars in the mailing cost corresponds to an increase of how many pounds in the weight of the shipment?

\vspace{0.75em}

\choicebox{A}{2}
\choicebox{B}{2.5}
\choicebox{C}{4}
\choicebox{D}{5}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

If $\dfrac{a}{b} = 4.5$ and $\dfrac{a}{kb} = 12.5$, what is the value of $k$?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the given system of equations, $k$ is a constant. If the system has no solution, what is the value of $k$?

\vspace{0.5em}

\[
\begin{aligned}
-5x &= 8 - ky \\
18y + 5x &= -10x + 21
\end{aligned}
\]

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the given system of equations, $m$ is a constant. If the system has no solution, what is the value of $m$?

\vspace{0.5em}

\[
\begin{aligned}
\dfrac{4}{3} + \dfrac{5}{4}x &= 28y + \dfrac{5}{8}x \\
my &= \dfrac{1}{2}(5x - 8)
\end{aligned}
\]

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the given system of equations, $b$ is a constant. If the system has no solution, what is the value of $b$?

\vspace{0.5em}

\[
\begin{aligned}
\dfrac{3}{10}y + \dfrac{b}{3}x &= \dfrac{3}{4} - \dfrac{1}{5}y \\
\dfrac{3}{8}x + \dfrac{3}{5} &= -\dfrac{1}{4}y + \dfrac{8}{5}
\end{aligned}
\]

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the $xy$-plane, the point $(18, y)$ is a solution to the given system of inequalities. Which of the following could be the value of $y$?

\vspace{0.5em}

\[
\begin{aligned}
x + y &< 25 \\
2x - 3y &< 77
\end{aligned}
\]

\vspace{0.75em}

\choicebox{A}{$-14$}
\choicebox{B}{$-6$}
\choicebox{C}{7}
\choicebox{D}{11}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Tina works no more than 30 hours at a nail salon each week. She can do a manicure in 20 minutes and a pedicure in 30 minutes. Each manicure earns her \$25 and each pedicure earns her \$40, and she must earn at least \$900 to cover her expenses. If $m$ represents the number of manicures Tina does in a week and $p$ represents the number of pedicures she does in a week, which system of inequalities describes all possible values of $m$ and $p$ for which Tina covers her expenses?

\vspace{0.75em}

\choicebox{A}{$3m + 2p \leq 30$, $25m + 40p \geq 900$}
\choicebox{B}{$2m + 3p \leq 30$, $25m + 40p \geq 900$}
\choicebox{C}{$\dfrac{m}{3} + \dfrac{p}{2} \leq 30$, $25m + 40p \geq 900$}
\choicebox{D}{$\dfrac{m}{3} + \dfrac{p}{2} \geq 900$, $25m + 40p \leq 30$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

During hibernation, adult male black bears lose 6 to 12 pounds in weight each week. An adult male black bear weighed 580 pounds after 5 weeks of hibernation. Which of the following inequalities gives all possible values for the black bear's weight $w$, in pounds, after 15 weeks of hibernation?

\vspace{0.75em}

\choicebox{A}{$400 \leq w \leq 490$}
\choicebox{B}{$460 \leq w \leq 520$}
\choicebox{C}{$460 \leq w \leq 580$}
\choicebox{D}{$610 \leq w \leq 640$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A window repair specialist charges \$220 for the first two hours of repair plus an hourly fee for each additional hour. The total cost for 5 hours of repair is \$400. Which function $f$ gives the total cost, in dollars, for $x$ hours of repair, where $x \geq 2$?

\vspace{0.75em}

\choicebox{A}{$f(x) = 60x + 100$}
\choicebox{B}{$f(x) = 60x + 220$}
\choicebox{C}{$f(x) = 80x$}
\choicebox{D}{$f(x) = 80x + 220$}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

For each real number $r$, which of the following points lies on the graph of each equation in the $xy$-plane for the given system?

\vspace{0.5em}

\[
\begin{aligned}
8x + 7y &= 9 \\
24x + 21y &= 27
\end{aligned}
\]

\vspace{0.75em}

\choicebox{A}{$\left(r, \dfrac{-8r + 9}{7}\right)$}
\choicebox{B}{$\left(\dfrac{-8r + 9}{7}, r\right)$}
\choicebox{C}{$\left(\dfrac{-8r + 63}{7}, \dfrac{9r + 189}{7}\right)$}
\choicebox{D}{$\left(\dfrac{r}{3} + 9, \dfrac{-r}{3} + 27\right)$}
