\subsection*{2.2 Non Linear and Systems of Equations    }

\vspace{0.5em}

\setcounter{questionnum}{0}


\noindent\markforreview
\vspace{1em}

What is the positive solution to the equation  
\(2|4 - x| + 3|4 - x| = 25\)?

\vspace{0.75em}



\vspace{5em}

\noindent\markforreview
\vspace{1em}

One solution to the equation \(x^2 - 2x - 9 = 0\)  
can be written as \(1 + \sqrt{k}\), where \(k\) is a constant.  
What is the value of \(k\)?

\vspace{0.75em}

\choicebox{A}{8}
\choicebox{B}{10}
\choicebox{C}{20}
\choicebox{D}{40}


\newpage
\noindent\markforreview
\vspace{1em}

In the \(xy\)-plane, a line with equation \(2y = 4.5\) intersects a parabola at exactly one point.  
If the parabola has equation \(y = -4x^2 + bx\), where \(b\) is a positive constant,  
what is the value of \(b\)?

\vspace{0.75em}



\vspace{5em}

\noindent\markforreview
\vspace{1em}

Given the system:
\[
\begin{cases}
x - y = 1 \\
x + y = x^2 - 3
\end{cases}
\]
Which ordered pair is a solution?

\vspace{0.75em}

\choicebox{A}{\((1 + \sqrt{3}, \sqrt{3})\)}
\choicebox{B}{\((\sqrt{3}, -\sqrt{3})\)}
\choicebox{C}{\((1 + \sqrt{5}, \sqrt{5})\)}
\choicebox{D}{\((\sqrt{5}, -1 + \sqrt{5})\)}




\newpage

\noindent\markforreview
\vspace{1em}

If \(x\) is a solution to the equation \(\frac{1}{x^2 + 10x + 25} = 4\),  
which of the following is a possible value of \(x + 5\)?

\vspace{0.75em}

\choicebox{A}{\(\frac{1}{2}\)}
\choicebox{B}{\(\frac{5}{2}\)}
\choicebox{C}{\(\frac{9}{2}\)}
\choicebox{D}{\(\frac{11}{2}\)}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

During a 5-second time interval, the average acceleration \(a\) (m/s²) of an object  
with an initial velocity of 12 m/s is defined by the equation  
\[
a = \frac{v_f - 12}{5}
\]  
If this is rewritten as \(v_f = xa + y\), what is the value of \(x\)?

\vspace{0.75em}

\newpage

\noindent\markforreview
\vspace{1em}

Which of the following is a solution to  
\(2x^2 - 2 = 2x + 3\)?

\vspace{0.75em}

\choicebox{A}{2}
\choicebox{B}{\(1 - \sqrt{11}\)}
\choicebox{C}{\(\frac{1}{2} + \sqrt{11}\)}
\choicebox{D}{\(\frac{1 + \sqrt{11}}{2}\)}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the \(xy\)-plane, a line with equation \(2y = c\) intersects a parabola  
\(y = -2x^2 + 9x\) at exactly one point.  
What is the value of \(c\)?

\vspace{0.75em}

\newpage


\noindent\markforreview
\vspace{1em}

What is the smallest solution to the equation  
\[
\sqrt{(x - 2)^2} = \sqrt{3x + 34}
\]

\vspace{0.75em}



\vspace{5em}

\noindent\markforreview
\vspace{1em}

Given the equation  
\[
57x^2 + (57b + a)x + ab = 0
\]  
where \(a\) and \(b\) are positive constants. The product of the solutions is \(kab\).  
What is the value of \(k\)?

\vspace{0.75em}

\choicebox{A}{\(\frac{1}{57}\)}
\choicebox{B}{\(\frac{1}{19}\)}
\choicebox{C}{1}
\choicebox{D}{57}

\newpage
\noindent\markforreview
\vspace{1em}

In the equation \(-x^2 + bx - 676 = 0\),  
\(b\) is a positive integer and the equation has no real solution.  
What is the greatest possible value of \(b\)?

\vspace{0.75em}



\vspace{5em}

\noindent\markforreview
\vspace{1em}

If \(3x^2 - 18x - 15 = 0\), what is the value of \(x^2 - 6x\)?

\vspace{5em}



\noindent\markforreview
\vspace{1em}

In the equation \(2x^2 - 4x = t\), \(t\) is a constant.  
If the equation has no real solutions, which of the following could be the value of \(t\)?

\vspace{0.75em}

\choicebox{A}{-3}
\choicebox{B}{-1}
\choicebox{C}{1}
\choicebox{D}{3}

\newpage

\noindent\markforreview
\vspace{1em}

In the equation \(x(kx - 56) = -16\), \(k\) is an integer constant.  
If the equation has no real solution, what is the least possible value of \(k\)?

\vspace{3em}

\noindent\markforreview
\vspace{1em}

The equation \(\frac{14x}{7y} = 2\sqrt{w + 19}\)  
relates the distinct positive real numbers \(w, x,\) and \(y\).  
Which equation correctly expresses \(w\) in terms of \(x\) and \(y\)?

\vspace{0.75em}

\choicebox{A}{\(\sqrt\frac{x}{y} - 19\)}
\choicebox{B}{\(\sqrt\frac{28x}{14y} - 19\)}
\choicebox{C}{\(\left(\frac{x}{y}\right)^2 - 19\)}
\choicebox{D}{\(\left(\frac{28x}{14y}\right)^2 - 19\)}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Solve for \(x\): \(\sqrt{2x + 6} + 4 = x + 3\)  
What is the solution set of the equation above?

\vspace{0.75em}

\choicebox{A}{\(\{-1\}\)}
\choicebox{B}{\(\{5\}\)}
\choicebox{C}{\(\{-1, 5\}\)}
\choicebox{D}{\(\{0, -1, 5\}\)}



\noindent\markforreview
\vspace{1em}

The function \(f\), defined by  
\[
f(x) = -\frac{1}{2}(x - 4)^2 + 10
\]  
 If the function \(g\) (not shown) is defined by  
\(g(x) = -x + 10\), what is one possible value of \(a\) such that \(f(a) = g(a)\)?

\vspace{0.75em}



\vspace{5em}

\noindent\markforreview
\vspace{1em}

In the equation \(x^2 - 34x + c = 0\), \(c\) is a constant.  
The equation has no real solutions if \(c > n\).  
What is the least possible value of \(n\)?

\vspace{5em}

\noindent\markforreview
\vspace{1em}

In the equation \(-16x^2 - 8x + c = 0\), \(c\) is a constant.  
The equation has exactly one solution.  
What is the value of \(c\)?

\vspace{0.75em}

\newpage
\noindent\markforreview
\vspace{1em}

How many distinct real solutions does the equation \((x - 1)^2 = -4\) have?

\vspace{0.75em}

\choicebox{A}{Exactly one}
\choicebox{B}{Exactly two}
\choicebox{C}{Infinitely many}
\choicebox{D}{Zero}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

How many distinct real solutions does the equation  
\(5x^2 + 10x + 16 = 0\) have?

\vspace{0.75em}

\choicebox{A}{Exactly one}
\choicebox{B}{Exactly two}
\choicebox{C}{Infinitely many}
\choicebox{D}{Zero}



\newpage

\noindent\markforreview
\vspace{1em}

Given the system:  
\[
\begin{cases}
y = x^2 + 2x + 1 \\
x + y + 1 = 0
\end{cases}
\]  
If \((x_1, y_1)\) and \((x_2, y_2)\) are the two solutions to the system,  
what is the value of \(y_1 + y_2\)?

\vspace{0.75em}

\choicebox{A}{-3}
\choicebox{B}{-2}
\choicebox{C}{-1}
\choicebox{D}{1}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

If \({u - 3} = \frac{6}{t - 2}\), what is \(t\) in terms of \(u\)?

\vspace{0.75em}

\choicebox{A}{\(\frac{1}{u}\)}
\choicebox{B}{\(\frac{2u + 9}{u}\)}
\choicebox{C}{\(\frac{1}{u - 3}\)}
\choicebox{D}{\(\frac{2u}{u - 3}\)}



\newpage

\noindent\markforreview
\vspace{1em}

In the equation \(-9x^2 + 30x + c = 0\), \(c\) is a constant.  
The equation has exactly one solution.  
What is the value of \(c\)?

\vspace{0.75em}

\choicebox{A}{3}
\choicebox{B}{0}
\choicebox{C}{-25}
\choicebox{D}{-53}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In the equation  
\[
\frac{x^2}{\sqrt{x^2 - c^2}} = \frac{c^2}{\sqrt{x^2 - c^2}} + 39,
\]  
where \(c\) is a positive constant, which of the following is one of the solutions?

\vspace{0.75em}

\choicebox{A}{\(-c\)}
\choicebox{B}{\(-c^2 - 39^2\)}
\choicebox{C}{\(-\sqrt{39^2 - c^2}\)}
\choicebox{D}{\(-\sqrt{c^2 + 39^2}\)}




\newpage


\noindent\markforreview
\vspace{1em}

The graphs of the equations  
\[
\begin{cases}
8x + y = -11 \\
2x^2 = y + 341
\end{cases}
\]  
intersect at the point \((x, y)\) in the \(xy\)-plane. What is a possible value of \(x\)?

\vspace{0.75em}

\choicebox{A}{-15}
\choicebox{B}{-11}
\choicebox{C}{2}
\choicebox{D}{8}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

What is the sum of the solutions to the equation  
\[
x(x + 1) - 56 = 4x(x - 7)?
\]

\vspace{0.75em}

\newpage

\noindent\markforreview
\vspace{1em}

In the \(xy\)-plane, the graph of \(y = x^2 - 9\) intersects line \(p\) at \((1, a)\) and \((5, b)\),  
where \(a\) and \(b\) are constants. What is the slope of line \(p\)?

\vspace{0.75em}

\choicebox{A}{6}
\choicebox{B}{2}
\choicebox{C}{-2}
\choicebox{D}{-6}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The formula  
\[
D = T - \frac{9}{25}(100 - H)
\]  
approximates the dew point \(D\) in Fahrenheit, given temperature \(T\) in Fahrenheit,  
and relative humidity \(H\%\), where \(H > 50\).  
Which of the following expresses \(H\) in terms of \(D\) and \(T\)?

\vspace{0.75em}

\choicebox{A}{\(H = \frac{25}{9}(D - T) + 100\)}
\choicebox{B}{\(H = \frac{25}{9}(D - T) - 100\)}
\choicebox{C}{\(H = \frac{25}{9}(D + T) + 100\)}
\choicebox{D}{\(H = \frac{25}{9}(D + T) - 100\)}

\newpage
\noindent\markforreview
\vspace{1em}

Given the equation  
\[
x - 29 = (x - a)(x - 29),
\]  
where \(a\) is a constant and \(a > 30\),  
which of the following are solutions?

I. \(a\) 

II. \(a + 1\) 

III. \(29\)

\vspace{0.75em}

\choicebox{A}{I and II only}
\choicebox{B}{I and III only}
\choicebox{C}{II and III only}
\choicebox{D}{I, II, and III}


\vspace{2em}
\noindent\markforreview
\vspace{1em}

Given the system:  
\[
\begin{cases}
y = 2x^2 - 21x + 64 \\
y = 3x + a
\end{cases}
\]  
In the system of the equations, a is a constant. The graphs intersect at exactly one point \((x, y)\). What is the value of \(x\)?

\vspace{0.75em}

\choicebox{A}{-8}
\choicebox{B}{-6}
\choicebox{C}{6}
\choicebox{D}{8}

\newpage

\noindent\markforreview
\vspace{1em}

In the \(xy\)-plane, the graph of \(y = 3x^2 - 14x\) intersects the graph of \(y = x\)  
at the points \((0, 0)\) and \((a, a)\). What is the value of \(a\)?


\vspace{5em}

\noindent\markforreview
\vspace{1em}

Given the equation  
\[
64x^2 - (16a + 4b)x + ab = 0
\]  
The sum of the solutions is \(k(4a + b)\). What is the value of \(k\)?





\vspace{5em}

\noindent\markforreview
\vspace{1em}

What is the sum of the solutions to the equation  
\[
x^2 - 40x - 10 = 0
\]

\vspace{0.75em}

\choicebox{A}{0}
\choicebox{B}{5}
\choicebox{C}{10}
\choicebox{D}{40}

\newpage


\noindent\markforreview
\vspace{1em}

Given the system:  
\[
\begin{cases}
y = x^2 + 3x - 7 \\
y - 5x + 8 = 0
\end{cases}
\]  
How many solutions are there?

\vspace{0.75em}

\choicebox{A}{Exactly 4}
\choicebox{B}{Exactly 2}
\choicebox{C}{Exactly 1}
\choicebox{D}{None}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Solve for \(x\):  
\[
\frac{4x^2}{x^2 - 9} - \frac{2x}{x + 3} = \frac{1}{x - 3}
\]

\vspace{0.75em}

\choicebox{A}{-3}
\choicebox{B}{\(-\frac{1}{2}\)}
\choicebox{C}{\(\frac{1}{2}\)}
\choicebox{D}{3}


\newpage


\noindent\markforreview
\vspace{1em}

Given the equation  
\[
64x^2 + bx + 25 = 0
\]  
For which of the following values of \(b\) will the equation have more than one real solution?

\vspace{0.75em}

\choicebox{A}{-91}
\choicebox{B}{-80}
\choicebox{C}{5}
\choicebox{D}{40}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Given the system:  
\[
\begin{cases}
y = -1.5 \\
y = x^2 + 8x + a
\end{cases}
\]  
If the system has exactly one real solution, what is the value of \(a\)?

\vspace{0.75em}

\newpage 

\noindent\markforreview
\vspace{1em}

In the \(xy\)-plane, the graph of \(y = -x^2 + 9x - 100\)  
intersects the line \(y = c\) at exactly one point.  
What is the value of \(c\)?

\vspace{0.75em}

\choicebox{A}{\(-\frac{481}{4}\)}
\choicebox{B}{-100}
\choicebox{C}{\(-\frac{319}{4}\)}
\choicebox{D}{\(-\frac{9}{2}\)}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Given the system:  
\[
\begin{cases}
x^2 + y + 7 = 7 \\
20x + 100 - y = 0
\end{cases}
\]  
The solution is \((x, y)\). What is the value of \(x\)?




\newpage 

