\subsection*{3.1 Ratios, Rates, Proportional Relationships, and Units}
\noindent\markforreview
\vspace{1em}

\textbf{Species of tree and Growth factor}
\begin{center}
    

\begin{tabular}{|l|c|}
\hline
\textbf{Species of tree} & \textbf{Growth factor} \\
\hline
Red maple & 4.5 \\
River birch & 3.5 \\
Cottonwood & 2.0 \\
Black walnut & 4.5 \\
White birch & 5.0 \\
American elm & 4.0 \\
Pin oak & 3.0 \\
Shagbark hickory & 7.5 \\
\hline
\end{tabular}
\end{center}

\vspace{1em}

One method of calculating the approximate age, in years, of a tree of a particular species is to multiply the diameter of the tree, in inches, by a constant called the growth factor for that species.  
The table above gives the growth factors for eight species of trees.  
If a white birch tree and a pin oak tree each now have a diameter of 1 foot, which of the following will be closest to the difference, in inches, of their diameters 10 years from now?  
(1 foot = 12 inches)

\vspace{0.75em}

\choicebox{A}{1.0}  
\choicebox{B}{1.2}  
\choicebox{C}{1.3}  
\choicebox{D}{1.4}

\newpage

\noindent\markforreview
\vspace{1em}

A sample of oak has a density of 807 kilograms per cubic meter.  
The sample is in the shape of a cube, where each edge has a length of 0.90 meters.  
To the nearest whole number, what is the mass, in kilograms, of this sample?

\vspace{0.75em}

\choicebox{A}{588}  
\choicebox{B}{726}  
\choicebox{C}{897}  
\choicebox{D}{1,107}

\vspace{2em}


\noindent\markforreview
\vspace{1em}

Jeremy deposited $x$ dollars in his investment account on January 1, 2001.  
The amount of money in the account doubled each year until Jeremy had 480 dollars in his investment account on January 1, 2005.  
What is the value of $x$?

\newpage

\noindent\markforreview
\vspace{1em}

\textbf{Power capacity distribution by state}
\begin{center}
    

\begin{tabular}{|l|c|c|c|c|}
\hline
State & Low & Medium & High & Total \\
\hline
Texas & 4 & 2 & 3 & 9 \\
California & 1 & 0 & 1 & 2 \\
Oregon & 1 & 0 & 1 & 2 \\
Indiana & 0 & 2 & 0 & 2 \\
Colorado & 1 & 1 & 0 & 2 \\
Iowa & 2 & 0 & 0 & 2 \\
Oklahoma & 1 & 0 & 0 & 1 \\
\hline
Total & 10 & 5 & 5 & 20 \\
\hline
\end{tabular}
\end{center}

\vspace{1em}

The table shows the distribution, by location and power capacity (maximum rate of power generation) of the twenty largest wind projects in the United States in 2013.  
The total power capacity of the nine wind projects located in Texas was 4,952 megawatts (MW), and the total power capacity of the twenty wind projects was 11,037 MW in 2013.  
The amount of energy produced in one hour at a rate of one megawatt is one megawatt-hour.  
If each of the nine Texas wind projects in 2013 had operated continuously for 24 hours at the maximum rate of power generation, approximately how many megawatt-hours of energy would the nine projects have produced?

\vspace{0.75em}

\choicebox{A}{200}  
\choicebox{B}{5,000}  
\choicebox{C}{11,000}  
\choicebox{D}{120,000}

\vspace{2em}
\newpage
\noindent\markforreview
\vspace{1em}

If $\frac{4a}{b} = 6.7$ and $\frac{a}{bn} = 26.8$, what is the value of $n$?

\vspace{0.75em}


\vspace{2em}

\noindent\markforreview
\vspace{1em}

The density of a certain type of wood is 353 kilograms per cubic meter.  
A sample of this type of wood is in the shape of a cube and has a mass of 345 kilograms.  
To the nearest hundredth of a meter, what is the length of one edge of this sample?

\vspace{0.75em}

\choicebox{A}{0.98}  
\choicebox{B}{0.99}  
\choicebox{C}{1.01}  
\choicebox{D}{1.02}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A certain town has an area of 4.36 square miles.  
What is the area, in \textbf{square yards}, of this town?  
(1 mile = 1,760 yards)

\vspace{0.75em}

\choicebox{A}{404}  
\choicebox{B}{7,674}  
\choicebox{C}{710,459}  
\choicebox{D}{13,505,536}

\newpage

\noindent\markforreview
\vspace{1em}

Anita created a batch of green paint by mixing 2 ounces of blue paint with 3 ounces of yellow paint.  
She must mix a second batch using the same ratio of blue and yellow paint as the first batch.  
If she uses 5 ounces of blue paint for the second batch, how much yellow paint should Anita use?

\vspace{0.75em}

\choicebox{A}{Exactly 5 ounces}  
\choicebox{B}{3 ounces more than the amount of yellow paint used in the first batch}  
\choicebox{C}{1.5 times the amount of yellow paint used in the first batch}  
\choicebox{D}{1.5 times the amount of blue paint used in the second batch}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A certain park has an area of 11,863,808 square yards.  
What is the area, in \textbf{square miles}, of this park?  
(1 mile = 1,760 yards)

\vspace{0.75em}

\choicebox{A}{1.96}  
\choicebox{B}{3.83}  
\choicebox{C}{3,444.39}  
\choicebox{D}{6,740.8}

\newpage
