\subsection*{3.5 Probability and Conditional Probability}

\vspace{0.5em}

\setcounter{questionnum}{0}


\noindent\markforreview

\begin{center}
\textbf{Number of Contestants by Score and Day}
\end{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
 & 5 out of 5 & 4 out of 5 & 3 out of 5 & 2 out of 5 & 1 out of 5 & 0 out of 5 & Total \\
\hline
Day 1 & 2 & 3 & 4 & 6 & 3 & 2 & 20 \\
Day 2 & 2 & 5 & 5 & 4 & 2 & 2 & 20 \\
Day 3 & 3 & 1 & 4 & 6 & 4 & 2 & 20 \\
\hline
Total & 7 & 9 & 13 & 16 & 9 & 6 & 60 \\
\hline
\end{tabular}

\vspace{1em}

The same 20 contestants, on each of 3 days, answered 5 questions in order to win a prize.  
Each contestant received 1 point for each correct answer. The number of contestants receiving a given score on each day is shown in the table above.  

No contestant received the same score on two different days.  
If a contestant is selected at random, what is the probability that the selected contestant received a score of 5 on Day 2 or Day 3, given that the contestant received a score of 5 on one of the three days?

\vspace{0.75em}



\vspace{2em}

\noindent\markforreview


\begin{center}
\textbf{Blood type}
\end{center}
\begin{center}
    

\begin{tabular}{|c|c|c|c|c|}
\hline
Rhesus factor & A & B & AB & O \\
\hline
+ & 33 & 9 & 3 & 37 \\
-- & 7 & 2 & 1 & $x$ \\
\hline
\end{tabular}
\end{center}

\vspace{1em}

Human blood can be classified into four common blood types—A, B, AB, and O.  
It is also characterized by the presence ($+$) or absence ($-$) of the rhesus factor.  
The table above shows the distribution of blood type and rhesus factor for a group of people.  
If one of these people who is rhesus negative ($-$) is chosen at random, the probability that the person has blood type B is $\frac{1}{9}$.  
What is the value of $x$?

\vspace{0.75em}


\vspace{2em}

\newpage
\noindent\markforreview

\begin{center}
    

\textbf{Preferred Activity by Response Type (Percent)}

\vspace{0.5em}
\begin{tabular}{|l|c|c|}
\hline
Activity & Phone & Email \\
\hline
Dinner dance & 55\% & 80\% \\
Football game & 20\% & 10\% \\
Picnic & 20\% & 5\% \\
Pool party & 5\% & 5\% \\
\hline
Total & 100\% & 100\% \\
\hline
\end{tabular}
\end{center}


An alumni association survey asked each high school graduate to select the one activity he or she preferred for the association’s next event.  
Some of the people responded by phone, and the others responded by email.  
For the survey, the number of email responses was twice the number of phone responses.  
If a person who preferred a picnic is selected at random, what is the probability that the person responded by email?



\vspace{2em}

\noindent\markforreview
\vspace{1em}

On May 10, 2015, there were 83 million Internet subscribers in Nigeria.  
The major Internet providers were MTN, Globacom, Airtel, Etisalat, and Visafone.  
By September 30, 2015, the number of Internet subscribers in Nigeria had increased to 97 million.  
If an Internet subscriber in Nigeria on September 30, 2015, is selected at random, the probability that the person selected was an MTN subscriber is 0.43.  
There were $p$ million MTN subscribers in Nigeria on September 30, 2015.  
To the nearest integer, what is the value of $p$?

\vspace{0.75em}

\vspace{2em}


\noindent\markforreview

\begin{center}
    

\textbf{Distribution of Age and Assigned Group}

\vspace{0.5em}

\begin{tabular}{|l|c|c|c|c|}
\hline
 & 0--9 years & 10--19 years & 20+ years & Total \\
\hline
Group A & 7 & 14 & 9 & 30 \\
Group B & 6 & 4 & 20 & 30 \\
Group C & 17 & 12 & 1 & 30 \\
\hline
Total & 30 & 30 & 30 & 90 \\
\hline
\end{tabular}
\end{center}

\vspace{1em}

One of these participants will be selected at random.  
What is the probability of selecting a participant from group A, given that the participant is at least 10 years of age?  
(Express your answer as a decimal or fraction, not as a percent.)

\vspace{0.75em}


\vspace{2em}


\newpage
\noindent\markforreview


\begin{center}
    

\textbf{2013 State-Level Taxes}

\vspace{0.5em}

\begin{tabular}{|l|c|c|}
\hline
 & State sales tax & No state sales tax \\
\hline
State income tax & 39 & 4 \\
No state income tax & 6 & 1 \\
\hline
\end{tabular}
\end{center}

\vspace{1em}

To the nearest tenth of a percent, what percent of states with a state-level sales tax do \textbf{not} have a state-level income tax?

\vspace{0.75em}

\choicebox{A}{6.0\%}  
\choicebox{B}{12.0\%}  
\choicebox{C}{13.3\%}  
\choicebox{D}{14.0\%}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Employees working for a customer service line at an electric company recorded all the calls last Monday and noted whether the caller asked for repairs and whether the caller asked about a bill.  
The results are summarized in the table below.

\vspace{0.75em}

\begin{tabular}{|l|c|c|c|}
\hline
 & Asked for repairs & Did not ask for repairs & Total \\
\hline
Asked about a bill & 48 & 623 & 671 \\
Did not ask about a bill & 130 & 90 & 220 \\
\hline
Total & 178 & 713 & 891 \\
\hline
\end{tabular}

\vspace{1em}

If a caller last Monday who asked about his or her bill is selected at random, which of the following is closest to the probability that the customer also asked for repairs?

\vspace{0.75em}

\choicebox{A}{0.05}  
\choicebox{B}{0.07}  
\choicebox{C}{0.20}  
\choicebox{D}{0.27}

\newpage
