\subsection*{Unit 3 Problem Solving and Data Practice Test}

\setcounter{questionnum}{0}

\noindent\markforreview
\vspace{1em}

The number \(p\) is \(60\%\) of the positive number \(q\), and \(p\) is \(390\%\) of the number \(r\).  
If \(q\) is \(x\%\) of \(r\), what is the value of \(x\)?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

At an auction, the starting price of a gemstone is set at \(60\%\) less than its assessed value of \(\$30{,}000\).  
Eli makes an offer that is \(370\%\) of the starting price.  
What is the value of Eli's offer, in dollars?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The number \(r\) is \(70\%\) less than the number \(s\).  
The number \(r\) is \(60\%\) greater than the number \(t\).  
If \(s = 180\), what is the value of \(t\)?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The number \(x\) is \(75\%\) less than the positive number \(y\).  
The number \(z\) is \(84\%\) greater than \(x\).  
The number \(z\) is how many times \(y\)?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

In 2010, the number of houses built in Town A was \(n\) percent greater than the number of houses built in Town B.  
If \(700\) houses were built in Town A in 2010, which expression represents the number of houses built in Town B in 2010?

\choicebox{A}{\(700 \left( \frac{100 + n}{100} \right)\)}  
\choicebox{B}{\(700 \left( \frac{100}{100 + n} \right)\)}  
\choicebox{C}{\(700 \left( \frac{100 - n}{100} \right)\)}  
\choicebox{D}{\(700 \left( \frac{100}{100 - n} \right)\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The area of Wompatuck State Park in Massachusetts is \(5.5\) square miles.  
Which of the following is closest to the area of this park, in square kilometers?  
(Use \(1\) kilometer \(= 0.62\) mile.)

\choicebox{A}{\(2.1\)}  
\choicebox{B}{\(3.4\)}  
\choicebox{C}{\(8.9\)}  
\choicebox{D}{\(14.3\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

If \(a\) apples cost \(d\) dollars, which of the following expressions gives the cost of \(20\) apples, in dollars?

\choicebox{A}{\(\frac{20a}{d}\)}  
\choicebox{B}{\(\frac{20d}{a}\)}  
\choicebox{C}{\(20d\)}  
\choicebox{D}{\(\frac{20}{ad}\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A model of a building has a scale where a width of \(5\) inches in the model represents an actual width of \(16\) feet.  
A room in the building has an actual width of \(10w\) feet.  
Which expression represents the width, in inches, of the room in the model?

\choicebox{A}{\(\frac{5}{8}w\)}  
\choicebox{B}{\(\frac{25}{8}w\)}  
\choicebox{C}{\(8w\)}  
\choicebox{D}{\(32w\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

An object is expanding so that its surface area is increasing at a constant rate of \(3\) square inches per hour.  
There are \(144\) square inches in \(1\) square foot.  
Of the following, which is closest to the rate at which the surface area of the object is increasing,  
in square meters per hour? (Use \(1\) foot \(= 0.3048\) meter.)

\choicebox{A}{\(0.0019\)}  
\choicebox{B}{\(0.0064\)}  
\choicebox{C}{\(0.0684\)}  
\choicebox{D}{\(0.2242\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A cheese vendor currently has \(175\) pounds of mozzarella available for sale.  
If each pound of mozzarella sells for \(\$8.75\), which of the following functions gives the amount of mozzarella \(M\),  
in pounds, still available for sale after \(d\) dollars worth has been sold?

\choicebox{A}{\(M(d) = 175 - \frac{d}{8.75}\)}  
\choicebox{B}{\(M(d) = 175 - 8.75d\)}  
\choicebox{C}{\(M(d) = 175 - \frac{8.75}{d}\)}  
\choicebox{D}{\(M(d) = 175(8.75) - d\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

Marcia baked \(240\) cookies and distributed a third of them evenly among \(c\) classmates.  
Each classmate received \(4\) cookies.  
Which equation represents this situation?

\choicebox{A}{\(\frac{3c}{240} = 4\)}  
\choicebox{B}{\(\frac{240c}{3} = 4\)}  
\choicebox{C}{\(\frac{240}{3c} = 4\)}  
\choicebox{D}{\(\frac{240(3)}{c} = 4\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A taxicab charges \(\$4.75\) for the first mile traveled and \(\$3.50\) for each additional mile.  
A particular passenger travels \(x\) miles in the taxicab and is charged a total of \(\$24\).  
Which equation represents this situation?

\choicebox{A}{\(3.50x - 4.75 = 24\)}  
\choicebox{B}{\(8.25x - 3.50 = 24\)}  
\choicebox{C}{\(3.50x + 1.25 = 24\)}  
\choicebox{D}{\(3.50x + 4.75 = 24\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A flask contains \(24\) milliliters of a \(30\%\) acid solution.  
How many milliliters of an \(8\%\) acid solution must be added to the flask to produce a \(16\%\) acid solution?

\vspace{2em}

\noindent\markforreview
\vspace{1em}

When ordering a certain book in bulk, a school pays \(\$1{,}720\) for the first \(80\) copies  
and a discounted price for each additional copy.  
The total cost for \(200\) copies of the book is \(\$3{,}700\).  
Which function \(f\) gives the total cost, in dollars, for \(x\) copies of the book, where \(x \geq 80\)?

\choicebox{A}{\(f(x) = 18.50x + 240\)}  
\choicebox{B}{\(f(x) = 18.50x + 1{,}720\)}  
\choicebox{C}{\(f(x) = 16.50x + 400\)}  
\choicebox{D}{\(f(x) = 16.50x + 1{,}720\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A tub can be filled by a hose and emptied by a drain.  
When the drain is closed, the hose can fill \(\frac{1}{3}\) of the tub in \(1\) minute.  
When the hose is turned off, the drain can empty \(\frac{2}{11}\) of the tub in \(1\) minute.  
If it takes \(t\) minutes for the hose to fill the tub while the drain is open,  
which of the following equations represents this situation?

\choicebox{A}{\(\frac{1}{3}t - \frac{2}{11} = 1\)}  
\choicebox{B}{\(\frac{1}{3} - \frac{2}{11} = \frac{1}{t}\)}  
\choicebox{C}{\(\frac{1}{3}t + \frac{2}{11} = 1\)}  
\choicebox{D}{\(\frac{1}{3} + \frac{2}{11} = \frac{1}{t}\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A manufacturer uses two assembly lines to produce refrigerator units.  
The table summarizes the results of a quality control test used to check for defective units.  
If a refrigerator unit that was checked during this test is selected at random,  
what is the probability that the unit was produced by assembly line A, given that the unit is defective?

\[
\begin{array}{|c|c|c|c|}
\hline
& \text{Defective} & \text{Not defective} & \text{Total} \\
\hline
\text{Assembly line A} & 300 & 5700 & 6000 \\
\text{Assembly line B} & 500 & 3500 & 4000 \\
\hline
\text{Total} & 800 & 9200 & 10000 \\
\hline
\end{array}
\]

\choicebox{A}{\(\frac{1}{20}\)}  
\choicebox{B}{\(\frac{3}{8}\)}  
\choicebox{C}{\(\frac{3}{5}\)}  
\choicebox{D}{\(\frac{5}{8}\)}  

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The table shows the results of a survey in which students at three colleges were asked whether they live on campus or off campus.  
If one of the students surveyed is selected at random, which of the following probabilities has the greatest value?

\[
\begin{array}{|c|c|c|c|}
\hline
& \text{Off campus} & \text{On campus} & \text{Total} \\
\hline
\text{College A} & 335 & 689 & 1024 \\
\text{College B} & 124 & 482 & 606 \\
\text{College C} & 596 & 274 & 870 \\
\hline
\text{Total} & 1055 & 1445 & 2500 \\
\hline
\end{array}
\]

\choicebox{A}{The probability that the student lives off campus, given that the student attends College C.}  
\choicebox{B}{The probability that the student lives on campus, given that the student attends College C.}  
\choicebox{C}{The probability that the student attends College C, given that the student lives off campus.}  
\choicebox{D}{The probability that the student attends College C, given that the student lives on campus.} 

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A researcher wanted to determine whether studying at a library is more effective than studying at home. He selected a random sample of 200 students and gave them three days to study for the same test. The 100 students who lived closest to a library were asked to study at a library, and the remaining 100 students were asked to study at home. After the students took the test, the scores of those who studied at a library were compared to the scores of those who studied at home. How should this experiment be changed so that the researcher can conclude whether studying at a library is more effective than studying at home?

\choicebox{A}{The students assigned to study at a library should study at the same library.}  
\choicebox{B}{The students should be randomly assigned to study either at a library or at home.}  
\choicebox{C}{The students assigned to study at a library should take a more difficult test than the students assigned to study at home.}  
\choicebox{D}{No changes to the experiment are necessary.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

A group of school administrators wanted to gather opinions on new teacher certification requirements that were introduced in a certain state. The group surveyed a random sample of math teachers from one of the school districts in the state. The survey showed that the majority of the teachers in the sample support the new requirements. Which of the following is the largest population to which the results of the survey can be generalized?

\choicebox{A}{All math teachers in the school district.}  
\choicebox{B}{All teachers in the school district.}  
\choicebox{C}{All math teachers in the state.}  
\choicebox{D}{The teachers in the sample.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

All the residents of a town were mailed a survey about proposed renovations to the town's high school. Approximately $10\%$ of the residents completed the survey and mailed it back. Based on the responses, it was estimated that $72\%$ of the residents support the proposed renovations, with an associated margin of error of $12\%$. Which of the following best explains why these survey results are unlikely to represent the opinions of all the town's residents?

\choicebox{A}{The survey included residents who do not attend the high school.}  
\choicebox{B}{Not all residents were aware of the proposed renovations before the survey.}  
\choicebox{C}{Responses to the survey were not obtained from a random sample of the town's residents.}  
\choicebox{D}{The margin of error is greater than the percentage of residents who responded to the survey.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The tables give the distribution of daily travel times between two towns for bus A and bus B over a 40-day period.

\[
\begin{array}{c|c}
\text{Travel time (minutes)} & \text{Frequency} \\
\hline
\textbf{Bus A} & \\
44 & 5 \\
45 & 10 \\
47 & 15 \\
48 & 10 \\
\hline
\textbf{Bus B} & \\
25 & 5 \\
30 & 10 \\
35 & 15 \\
40 & 10 \\
\end{array}
\]

Which statement correctly compares the standard deviations of travel times for bus A and bus B?

\choicebox{A}{The standard deviation of travel times for bus A is less than the standard deviation of travel times for bus B.}  
\choicebox{B}{The standard deviation of travel times for bus B is less than the standard deviation of travel times for bus A.}  
\choicebox{C}{The standard deviation of travel times for bus A is equal to the standard deviation of travel times for bus B.}  
\choicebox{D}{There is not enough information to compare these standard deviations.}

\vspace{2em}

\noindent\markforreview
\vspace{1em}

The employees at a new bookstore must stock a certain number of shelves so that the store is ready for its opening in two weeks. The employees stock shelves at a constant rate throughout the two weeks. If $p(t)$ is the number of shelves left to be stocked after $t$ days, which of the following statements best describes the function $p$?

\choicebox{A}{The function $p$ is an increasing exponential function.}  
\choicebox{B}{The function $p$ is a decreasing exponential function.}  
\choicebox{C}{The function $p$ is an increasing linear function.}  
\choicebox{D}{The function $p$ is a decreasing linear function.}
